---
title: "Gun Control Chi-Square"
author: "Adrienne Hewitt"
date: "November 14, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm Adrienne and I'm adding some text ehre to see id Shellby can get this file. 

Beep Beep. I am updating text. 

My turn to add a little something. 


Adrienne:
Getting the gc_df.csv data, loading the tidyverse, and getting some summary counts
```{r}
library(tidyverse)
gc_df<-read_csv("gc_df.csv")
gc_df


get_guns<-gc_df %>%
  filter(gender!="NA", make_get_guns!="NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>%
  select(-gender)


rownames(get_guns)<- c("female", "male")


```

I'm the collaborator (Shellbs) and I am going to do Chi-square.

Is there a significant difference in gun control perspectives as related to access to guns for male and females?

OR

Is there a significant association between sex and gun control recommendations?

OR

Is perception of gun control access independent of sex?


Chi-Square
```{r}

guns_prop <- prop.table(as.matrix(get_guns), 1)
guns_prop


#Perfoming chi-square

guns_x2 <- chisq.test(get_guns)
guns_x2



```


Recommended government action on gun access differs significantly for males and females ($\chi^2$(`r guns_x2$parameter`)) = ....., p <0.001)




